---
title: "R Notebook"
output: html_notebook
---

Read the data set mtcars in R. It gives a comparison between different car models in terms of
mileage per gallon mpg, cylinder displacement disp, horse power , weight of the car wt and
some more parameters.
1. Create a subset of the variables mpg, disp, hp and wt from the mtcars data. Construct
the scatter plot for these attributes

```{r}
install.packages('dplyr')
library(dplyr)
library(explore)
```


```{r}
subset_mtcars <- mtcars[,c("mpg","disp","hp","wt")]
print(head(subset_mtcars))
```



```{r}
plot(subset_mtcars)
```

```{r}
summary(lm (mpg ~ disp + hp , data = mtcars ))
```


3. Create two multiple linear regression models having both mpg as output, and disp+hp
and disp+hp+wt as input variables respectively. Discuss the significance of these two
models by running ANOVA which compares residuals.
```{r}
reduced = lm (mpg ~ disp + hp , data = mtcars )
summary(reduced)

```
```{r}
full = lm ( mpg ~ disp + hp + wt , data = mtcars )
summary(full)

```
```{r}
anova(reduced, full)
```

